%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Site Reliability Engineer} % Job title
    {Atlassian.} % Organization
    {Bengaluru,India} % Location
    {June. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
               \item { Worked on creating Opentelemetry Libararies and Middleware for golang applications }
               \item { Worked on standardizing Visualizations,SLIs, Alerts and Dashboards using terraform modules and terraform-cdk} 		
	  \end{cvitems}
    }
    \cventry
    {Core Software Engineer} % Job title
    {Tower Research Capital.} % Organization
    {Gurugram,India} % Location
    {July. 2019 - June. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item { Responsible for monitoring of  Kubernetes clusters using Prometheus(Prometheus Operator) and Elk stack }
               \item { Responsible for maintaining  Kafka clusters on Kubernetes using  Strimzi Kafka Operator }
               \item { Onboarding logging pipelines for various teams using Kafka and Elk stack }
               \item { Developed helm charts for various Application metric exporters for monitoring applications  }
               \item { Worked on deploying and maintaining Elasticsearch clusters with role based access(searchguard,opendistro) , ratelimiting(lua based proxy) and audit logging(searchguard)} 		
	  \end{cvitems}
    }
    \cventry
    {Software Engineer} % Job title
    {T-Systems ICT India Pvt Ltd.} % Organization
    {Gurugram,India} % Location
    {Aug. 2018 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item { Responsible for creating and maintaing Aws Vpc , IAM and Vpn configurations}
		\item {Worked on CI/CD pipelines for IOS/ANDROID applications using Gitlab-CI (with Jira and Confluence integration for automating entire build and release process)}
		\item {Responsible for deploying and maintaing various Elasticsearch and Kafka clusters with role based access control }
		\item  { Responsible for Deployment and Designing the  Architecture for centralized logging platform for mobile devices}
		\item { Used Aws autoscaling along with custom scripts  for creating  a highly available and scalable   Rabbitmq cluster (serving as mqtt broker for mobile devices (logging infrastructure) }
		\item {Developed various  Aws Lambda based serverless applications for automation of various tasks }                   
	  \end{cvitems}
    }

  \cventry
    {Operations Engineer} % Job title
    {Media.net} % Organization
    {Mumbai,India} % Location
    {Jun. 2015 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Developed a custom tool and browser addon for Aws resource tagging and billing analysis }
		\item {Developed a custom dashboard for network traffic analysis using netflow and Elk stack }
        \item {Worked on various Logging applications using ELK(ElasticSearch, Logstash,Kibana) stack and Kafka}
        \item {Built fully automated CI/CD pipelines on Jenkins for various applications}
        \item {Implemented several production setups of a microservices based applications ( java, nodejs) with dockerized dependencies}
        \item {Worked on various logging and metric collection platforms and created app dashboards and alerts utilizing the data collected}
		\item {Implement various serverless Apis and functions using Aws lamda and Aws api gateway}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
